\documentclass[../../../00-main.tex]{subfiles}

\begin{document}


\section{Proofs}
\label{app:DF_R}

\subsection{Proposition 1}

\begin{proof}

\par Let
\[
W^{A}(\{p_s\};U) \equiv \min_{\lambda \in C} \int_S \big(\mathbb{E}_{p_s}[U]\big)\,d\lambda,
\qquad C \subseteq \Delta(S),\ C\neq\emptyset,
\]
and fix any $U$ with $U' > 0$ and $U'' \leq 0$.

\par Suppose that, for every state $s \in S$,
\[
\int_0^z \big[P_s(y)-P_s^*(y)\big]dy \le 0
\quad\text{for all } z\in[0,\bar y],
\]
where
\[
P_s(y)=\int_0^y p_s(t)\,dt,
\qquad
P_s^*(y)=\int_0^y p_s^*(t)\,dt.
\]

\par For each fixed state $s$, this is exactly the single-state second-order stochastic dominance condition. Hence,
\[
\mathbb{E}_{p_s}[U] \ge \mathbb{E}_{p_s^*}[U]
\quad\text{for every } s\in S.
\]

\par Let $\lambda\in C$ be arbitrary. Since $\lambda$ is a probability measure on $S$,
\[
\int_S \mathbb{E}_{p_s}[U] \, d\lambda
\ge
\int_S \mathbb{E}_{p_s^*}[U] \, d\lambda.
\]
Because this inequality holds for every $\lambda\in C$, taking minima over $C$ gives
\[
\min_{\lambda\in C}\int_S \mathbb{E}_{p_s}[U] \, d\lambda
\ge
\min_{\lambda\in C}\int_S \mathbb{E}_{p_s^*}[U] \, d\lambda.
\]
Therefore,
\[
W^{A}(\{p_s\};U) \ge W^{A}(\{p_s^*\};U).
\]
Since $U$ was arbitrary in the class $\{U: U'>0,\ U''\le 0\}$, the claim follows.

\end{proof}

\begin{remak}
The argument above establishes a sufficient condition. In general, the converse fails under a maxmin aggregator: the minimizing prior may assign zero weight to states where state-by-state dominance fails. An equivalence requires stronger assumptions (for example, comparisons for every $\lambda$ in a sufficiently rich set of priors that identifies each state).
\end{remak}

\subsection{Single-state benchmark}

\begin{prop}
For a single-state problem with distributions $f$ and $f^*$ on $[0,\bar y]$, define
\[
F(y)=\int_0^y f(t)\,dt,
\qquad
F^*(y)=\int_0^y f^*(t)\,dt.
\]
Then
\[
\mathbb{E}_{f}[U] \ge \mathbb{E}_{f^*}[U]
\quad\text{for all } U\text{ with }U'>0,\ U''\le 0
\]
if and only if
\[
\int_0^z \big[F(y)-F^*(y)\big]dy \le 0
\quad\text{for all } z\in[0,\bar y].
\]
Moreover, strict preference for all such $U$ requires strict inequality for some $z\in(0,\bar y)$.
\end{prop}

\subsection{Section 3.6 The Analogy between Income and Wealth Inequality Aversion}
\label{app:objective-benchmark}

\par To understand the problem, I begin with describing the model which proposes measures of income inequality using the choice under objective uncertainty literature. 

\subsubsection*{Analytical framework}

\par Denote the set of outcomes $Y = [0,\bar{y}]$. Then, the choice set is given by:

$$ L = \bigg\{ p: 2^{[0,\bar{y}]} \to \mathbb{R} \hspace{2mm} | \hspace{2mm} p(\cdot) \hspace{2mm} \text{is an income frequency distribution}  \bigg\}. $$

\par We may define a binary relation over both sets $Y,L:$

$$ \succsim_{y} \subseteq [0,\bar{y}] \times [0,\bar{y}] \subseteq \mathbb{R} \times \mathbb{R} $$

$$ \succsim \; \subseteq L \times L. $$

\par Notice that $\succsim_y$ may be represented by a real-valued utility function. This is the social welfare $U(y)$ which is a key object of analysis in this paper. 

\subsubsection*{Axiomatization}

\begin{ax.V}[Weak Order]
$\succsim$ is complete and transitive.
\end{ax.V}

\begin{ax.V}[Continuity]
For every $p(\cdot)$, $p^*(\cdot)$, $p'(\cdot)$ $\in L$, if $p(\cdot) \succ p^*(\cdot) \succ p'(\cdot) $, there exists $\alpha, \beta \in (0,1)$ such that 
$$ \alpha p + (1-\alpha)p' \succ p^* \succ \beta p + (1-\beta) p' .$$ 
\end{ax.V}

\begin{ax.V}[Independence]
For every $p,p^*,p' \in L$ and every $\alpha \in (0,1)$ such that 
$$ p \succsim p^* \iff \alpha p + (1-\alpha)p' \succsim \alpha p^* + (1-\alpha)p'. $$
\end{ax.V}

\subsubsection*{Expected utility representation of the ranking over income distributions}

\par The ranking over income distributions will be represented using the vNM-expected utility representation. That is,
$$ p(y) \sim \int_{0}^{\bar{y}} U(y) p(y) dy \equiv W^{O}. $$

\par Formally, note the slight modification of the vNM-EU theorem in this setting of ranking income distributions:

\begin{tm}
$\succsim \subseteq L \times L$ satisfies $(V1)$ \textbf{weak order}, $(V2)$ \textbf{continuity}, $(V3)$ \textbf{independence} if and only if there exists $U: Y \to \mathbb{R}$ such that, for every $p(y), p^*(y) \in L,$
$$ p(y) \succsim p^*(y) \iff \int_{0}^{\bar{y}} U(y) p(y) dy \geq \int_{0}^{\bar{y}} U(y) p^*(y) dy. $$
\end{tm}

\subsubsection*{3.6.1 Ratio measure $D$}

Recall the total social welfare under the two choice models: choice under objective uncertainty and choice under ambiguity. 
\[
W^{O} \equiv \int_0^{\bar y} U(y)\,p(y)\,dy
\]
\[
W^{A} \equiv \min_{\lambda\in C}\int_S \mathbb{E}_{p_s}[U] \, d\lambda.
\]
Then the ratio measures are
\[
D^{O} = \frac{W^{O}}{U(\mu)},
\qquad
D^{A} = \frac{W^{A}}{U(\mu)}.
\]


\subsubsection*{3.6.2 Equally distributed equivalent measure}

Define the EDE wealth levels by
\[
U\big(w_{EDE}^O\big)=W^{O} = \int_0^{\bar y} U(y)\,p(y)\,dy,
\qquad
U\big(w_{EDE}^A\big)= W^{A} = \min_{\lambda\in C}\int_S \mathbb{E}_{p_s}[U] \, d\lambda.
\]
Hence,
\[
w_{EDE}^O = U^{-1}(W^{O}),
\qquad
w_{EDE}^A = U^{-1}(W^{A}).
\]
The corresponding inequality measures are
\[
I^{O} = 1-\frac{w_{EDE}^O}{\mu},
\qquad
I^{A} = 1-\frac{w_{EDE}^A}{\mu}.
\]

\subsubsection*{3.6.3 Closed form under homothetic preferences}

For
\[
U(y)=
\begin{cases}
A + B\dfrac{y^{1-\epsilon}}{1-\epsilon}, & \epsilon\neq 1,\\
A + B\ln y, & \epsilon=1,
\end{cases}
\qquad B>0,
\]
we obtain the objective and ambiguity formulas by substituting the corresponding welfare aggregator.

If $\epsilon\neq 1$:
\[
w_{EDE}^O=\left[\frac{1-\epsilon}{B}\big(W^{O}-A\big)\right]^{\frac{1}{1-\epsilon}},
\qquad
w_{EDE}^A=\left[\frac{1-\epsilon}{B}\big(W^{A}-A\big)\right]^{\frac{1}{1-\epsilon}},
\]
\[
I^{O} = 1-\frac{1}{\mu}\left[\frac{1-\epsilon}{B}\big(W^{O}-A\big)\right]^{\frac{1}{1-\epsilon}},
\qquad
I^{A} = 1-\frac{1}{\mu}\left[\frac{1-\epsilon}{B}\big(W^{A}-A\big)\right]^{\frac{1}{1-\epsilon}}.
\]

If $\epsilon=1$:
\[
w_{EDE}^O=\exp\!\left(\frac{W^{O}-A}{B}\right),
\qquad
w_{EDE}^A=\exp\!\left(\frac{W^{A}-A}{B}\right),
\]
\[
I^{O} = 1-\frac{1}{\mu}\exp\!\left(\frac{W^{O}-A}{B}\right),
\qquad
I^{A} = 1-\frac{1}{\mu}\exp\!\left(\frac{W^{A}-A}{B}\right).
\]

\par So the extension from objective uncertainty to ambiguity is algebraically the replacement
\[
W^{O} \longrightarrow W^{A},
\]
with the EDE inversion and inequality-index algebra unchanged.


\end{document}
