\onlyinsubfile{\setcounter{section}{1}}
\section{Literature Review}
\label{sec:litrev}


\par This work builds on the literature interested in measures of trust and its determinants, empirical estimates of the rate of return in broad and narrow asset classes, and the statistical relationship between trust and economic performance. 

\subsection{Trust}

\par This paper draws on the literature on trust and its determinants. An example of this is \cite{Alesina2000}, who have the advantage of the standard demographic control variables (age, race, education, sex) as well as living in a community with significant heterogeneity in terms of race or income. My approach here is different in that I let the available survey responses in 2020 guide the set of demographic control variables used to explain the general trust measure, which can be found in the Appendix.  

%%%%%%%%%%%%%%%%%%%%%%%%%%

\par This main contribution of this paper to the literature is in relation to the empirical relationship between trust measures and economic performance.  \cite{lgpslz2008} finds that trust can lead to greater participation in the stock market. \cite{Guiso2004} finds that measures of social capital and trust lead to greater use of financial instruments such as checks, as well as diversification of the poor portfolio away from holding cash and towards holding stocks and other assets. The paper in this literature on trust and economic performance which serves as a key motivation is \cite{jbpglg2016}. The authors find that an intermediate level of trust is associated with the maximum level of income. The key difference between what is done there and my paper is that the measure of economic performance here is the return to net wealth: measures of returns using this dataset can be interpreted as an investor's performance in their financial contracting behavior within a given asset/portfolio class. Because returns to net wealth are thought to differ persistently between individuals over time, I focus on the panel structure of the HRS to describe the individual fixed effect for the return measure. 

 Although I focus on the general trust measure in this paper, there are other trust measures available in the HRS 2020 wave. \cite{Rosen2025} also uses this specially-designed trust module, although the authors focus on retirement security. They identify aggregate measures of trust; in particular, \textit{Trust in Financial Institutions} and also make use of the set of financial literacy questions available in that same wave; each of these serve as potential directions to test the robustness of the main result for trust and returns to net wealth. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

\par\cite{Alsan2018} find that the 1972 public revelation of the Tuskegee Syphilis Study led to  lower trust in black males in medical institutions, ultimately leading to worse health outcomes over a lifetime. \cite{Algan2010} find that aggregate trust has a large positive causal effect on GDP per capita by showing that a measure of inherited trust by second generation immigrants in the U.S. is strongly correlated with aggregate trust in the origin country (and is persistent across generations). These papers serve as inspiration for attempts at identifying the causal effects of trust on returns, although the HRS data was unfavorable in terms of results in this direction. 

 
\subsection{Returns}

\par An important work in the literature on empirical estimates of the rate of return is \cite{aflgdmlp20}. The authors provide estimates of the distribution of returns within narrowly defined asset classes and also characterize the persistent component of returns across individuals. The HRS RAND product is publicly available survey data, which is much lower in quality than the Norwegian population-level tax data available to those authors for their project. That said, we are able to produce estimates of the distribution of returns (for asset classes and portfolios) and the individual fixed effect for returns to net wealth, which can be directly compared to those same objects. The major deviation of my paper from this work is that  I complete these two tasks while controlling for the empirical relationship between trust and returns, which this paper makes no comment on. 

\par \cite{Daminato2024} also documents the persistent component of returns in the Panel Survey of Income Dynamics (PSID), and then uses the data to calibrate a return-earnings process within a life cycle model of consumption-saving behavior. The usefulness of this paper for my own work is that the authors present a standard method for computing returns using the PSID. Due to the PSID's structure being very similar to the HRS, I use the authors' definition of returns as a template to guide the definition of return measures using the HRS data. The major deviation of my paper from this work is also my interest in the trust measure (which the PSID does not measure in any wave of its survey).

\subsection{Panel regression techniques for time-invariant regressors}

\par The fact that the returns can be computed for multiple waves is essential to describe the persistent component in the returns between respondents. This, combined with the fact that the HRS only asks respondents about trust for a single wave of the survey, drives the empirical techniques chosen in this paper. In particular, trust must be treated as time-invariant to make use of the HRS data. Said differently, a regression model that accommodates both time-varying and time-invariant regressors is required to make use of the HRS data. \footnote{Assuming trust is time-invariant is not unreasonable -- there is empirical evidence to support this assumption.} 

\par Moreover, when the regressor of interest is time-invariant, it is no longer sufficient to extend the pooled regression environment to allow for individual fixed effects.\footnote{The education variable in the HRS (\textit{Years of Schooling}) is also treated as time-invariant in the RAND version of the dataset. Since education is generally thought of to be important for returns (or co-variates) dealing with time-invariant regressors in the panel setting is likely unavoidable when using the HRS.} Indeed, estimating the individual fixed effect prevents the model from estimating coefficients on any of the time-invariant regressors, since the term absorbs all latent time variation. This would be at odds with establishing a hump-shaped relationship between trust and returns using the data. This is the central econometric issue of this paper, and the following papers help to address it. \cite{BaltagiLiu2026Mundlak} offers an example of the general panel regression environment that fits the structure of HRS data well. The main panel regression models studied in this paper are the Fixed Effects (FE), Random Effects (RE), and Correlated Random Effects (CRE) models. \cite{Wooldridge2019CRE} offers a useful discussion on the Hausmann test and selecting among panel regression models. \cite{BollenBrand2010} focuses on the CRE/Mundlak version of the model where time-varying regressors are allowed to co-vary with the individual fixed effect component. 
